Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-03-30 paper_latex_edit - Copy.tex
txs auto checkin

\begin{equation}
	\hat{\textbf{H}}_{n}=\textbf{Y}_{p,n}\textbf{X}^{\dag}_{p,n}
\end{equation}
where 
\begin{math}
	\hat{\textbf{H}}_{n} \in C^{1\times N_{t}} 
\end{math} and
 \begin{math} \textbf{X}_{p,n}^{\dag}= \textbf{X}^{H}_{p,n}(\textbf{X}_{p,n}\textbf{X}^{H}_{p,n})^{-1} \end{math}.
For each subcarrier estimated CSI matrices is 
\begin{math}
	\{  \hat{\textbf{H}}_{1},...,\hat{\textbf{H}}_{N_{c}} \}
\end{math}.

@@

For simplicity we stack and reshape the channel matrix into:
\begin{equation}
		H_{freq}=\left[\hat{\textbf{H}}_{1}^{H},\hat{\textbf{H}}_{2}^{H},...,\hat{\textbf{H}}_{N_{c}}^{H}\right]^{H}_{N_{c}\times N_{t}}
\end{equation}

Evidently, \begin{math} H_{freq} \in C^{N_{c}\times N_{t}}\end{math} has \begin{math}\ 2\times N_{c}\times N_{t}\end{math} float numbers, which is too big for direct feedback in a massive MIMO system and this feedback is required for creating
the precoding to be built by base station.

@@

Where \begin{math}\gamma \end{math}, \begin{math}\ N_{s} \end{math}, \begin{math}\ N_{i} \end{math} and \begin{math}\ N_{t} \end{math} are compression ratio, codeword length, selected rows from \begin{math}\tilde{H} \end{math} and number of transmit antenna.

>>>>

\begin{equation}
	\hat{\textbf{H}}_{n}=\textbf{Y}_{p,n}\textbf{X}^{\dag}_{p,n}
\end{equation}
where 
\begin{math}
	\hat{\textbf{H}}_{n} \in C^{1\times N_{t}} 
\end{math} and
 \begin{math} \textbf{X}_{p,n}^{\dag}= \textbf{X}^{H}_{p,n}(\textbf{X}_{p,n}\textbf{X}^{H}_{p,n})^{-1} \end{math}.
 The pilot matrix \(\mathbf{X}_{p,n}\) satisfies \(\mathbf{X}_{p,n} \mathbf{X}_{p,n}^H = \mathbf{I}_{N_t}\) for \(T_p \geq N_t\).
For each subcarrier estimated CSI matrices is 
\begin{math}
	\{  \hat{\textbf{H}}_{1},...,\hat{\textbf{H}}_{N_{c}} \}
\end{math}.

@@

For simplicity we stack and reshape the channel matrix into:
\begin{equation}
	H_{freq}=\left[\hat{\textbf{H}}_{1}^{H},\hat{\textbf{H}}_{2}^{H},...,\hat{\textbf{H}}_{N_{c}}^{H}\right]^{H}_{N_{c}\times N_{t}}
\end{equation}
\(H_{\text{freq}} \in \mathbb{C}^{N_c \times N_t}\) is the stacked CSI matrix across subcarriers.
Evidently, \begin{math} H_{freq} \in C^{N_{c}\times N_{t}}\end{math} has \begin{math}\ 2\times N_{c}\times N_{t}\end{math} float numbers, which is too big for direct feedback in a massive MIMO system and this feedback is required for creating
the precoding to be built by base station.

@@

Where \begin{math}\gamma \end{math}, \begin{math}\ N_{s} \end{math}, \begin{math}\ N_{i} \end{math} and \begin{math}\ N_{t} \end{math} are compression ratio, codeword length, selected rows from \begin{math}\tilde{H} \end{math} and number of transmit antenna.where \(N_s\) is the real-valued codeword length, and \(2 N_i N_t\) accounts for the real/imaginary parts of \(\tilde{\mathbf{H}}_f\).
